Railway: Adaptive Disk Storage for Interaction Graphs

### 2014-09-18 docs/edbt2015/text/optimal.tex
first cut of the optimal railway design section is complete

HERE
The query I/O cost for a block is then given by:
\begin{equation}
L(\mathcal{P}, B) = \sum_{q\in Q} w(q)\cdot\mathbf{1}(q.T \cap B.T \neq \emptyset) \cdot \sum_{B'\in m(\mathcal{P}, B, q)} \!\!s(B')
\end{equation}

Here, $w(q)$ represents the query weight.

>>>>

Given that we have defined the function $m$ that maps a query to the set of 
sub-blocks used to answer it, we can now formalize the total query I/O cost
for a block under a given workload:
\begin{equation}
L(\mathcal{P}, B) = \sum_{q\in Q} w(q)\cdot\mathbf{1}(q.T \cap B.T \neq \emptyset) \cdot \sum_{B'\in m(\mathcal{P}, B, q)} \!\!s(B')
\end{equation}

We simply sum the I/O cost contributions of the queries to compute the total
I/O cost. A query contributes to the total I/O cost if and only if its time
range intersects with that of the block ($\mathbf{1}(q.T \cap B.T \neq
\emptyset)$). If it does, then we add the sizes of all the sub-blocks used to
answer the query to the total I/O cost. Furthermore, we multiply the I/O cost
contribution of a query with its frequency, denoted by $w(q)$ in the formula.
